---
title: 'Denominator Examples'
format:
  html:
    theme: flatly
    toc: true
    toc-depth: 4
    toc-title: "Table of Contents"
    toc-float:
      enabled: true
      offset-y: 50
      show: "scroll"
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(arrow)
library(data.table)

source('functions/fxn_assign_day_of_phase_group.R')
source('functions/fxn_add_event_counts.R')
source('functions/fxn_create_dop.R')

```




```{r}

denominator_base<-read_parquet('data/intermediate_files/denominator_by_calendar_time_period.parquet')

```

##  Example with lactation groups

This example uses calendar denominators, but the same concepts apply to time period denominators

### Step 1 - Select your denominator

The first step is to filter your denominator according to the `calendar_time_period_type` that you want. If you are using time period denominators this step is performed by the denominator file name you read in (file names contain the time period).

The options for calendar periods are: **`r sort(unique(denominator_base$calendar_time_period_type))`**

The second step is to choose your lactation and day of phase grouping. To simplify this first example will select a grouping without day of phase. (see the DOP section for day of phase examples)

The options for groups are: **`r sort(unique(denominator_base$deno_type))`**

Your final code should look something like this:

```{r, echo = TRUE}

denominator<-read_parquet('data/intermediate_files/denominator_by_calendar_time_period.parquet')%>%
  filter(calendar_time_period_type %in% 'month')%>% #choose denominator period type
  filter(deno_type %in% 'lact_3+')%>% #choose the type of lactation group
  distinct()%>%
  select(-contains('dop'), -day_of_phase_group) # day of phase columns are not needed when dop is not part of grouping

```

```{r}
head(denominator)
```
### Step 2 - Summarize your numerator correctly

Follow the comments documenting the steps for nummerator summary

```{r, echo = TRUE}

mast_event_summary<-read_parquet('data/intermediate_files/events_formatted.parquet')%>%
  
  #select event of interest
  filter(event %in% 'MAST')%>% 
  
  #add the event counts the way you like
  fxn_add_event_counts()%>% 
  mutate(event_count_lact = case_when(
    event_count_lact <4~paste0('Mast ', event_count_lact), 
    TRUE~'Mast 4+'
  ))%>%
  
  #match the dates to the denominator
  mutate(date_time_period_start = floor_date(date_event, unit = 'month'))%>% 
  
  #use same  lactation grouping as denominator (0, 1, 2, 3+), 
  #and set location to match denominator (locations will depend of farm data structure)
  mutate(`Lactation Group` = lact_group, 
         location_lact_list = location_event) %>% 
  
  #group by all variables in the denominator, plus any extras that you want (like event count), and summarize
  group_by(location_lact_list, `Lactation Group`, 
            date_time_period_start, event_count_lact)%>% 
  summarize(ct_mast_events = n_distinct(id_animal))%>%
  ungroup()
  

```

### Step 3 - Join denominator to numerator

```{r, echo = TRUE}
final_data<-denominator%>%
  left_join(mast_event_summary)%>%
  mutate(mast_rate = ct_mast_events/ct_animal_time_periods)

head(final_data)
```


### Step 4 - Look at results

```{r, echo = TRUE}

ggplot(final_data)+
  geom_point(aes(x = date_time_period_start, y= mast_rate, color = `Lactation Group`))+
    geom_smooth(aes(x = date_time_period_start, y= mast_rate, 
                    color = `Lactation Group`, group =  `Lactation Group`, 
                    fill = `Lactation Group`),alpha = .2 , span = .6)+

  facet_grid(event_count_lact~location_lact_list, scales = 'free')



```

## Example of adding DOP groups to lactation groups

The same steps apply as when using lactation groups, but in addition the day of phase group at the time of the event must be assigned.  You will notice that we selected a yearly denominator rather than monthly.  It is important to remember that when dop is used it creates many more categories so in general time periods should be longer if you are using DOP groups. 

### First, select your denominator. 

```{r, echo = TRUE}
denominator_dop<-read_parquet('data/intermediate_files/denominator_by_calendar_time_period.parquet')%>%
  filter(calendar_time_period_type %in% 'year')%>% #choose denominator period type
  filter(deno_type %in% 'dop_lact_3+')%>% #choose the type of lactation group
  distinct() 


```

### Next Then summarize events according to denominator.

In order to summarize correctly, you need to match the dop groups in the denominator, so the first step is to create a lookup table from your denominator.


#### Create a lookup table

```{r, echo = TRUE}

  lookup_dop<-denominator_dop%>%
  select(`Lactation Group`, day_of_phase_group, contains('dop'))%>%
  select(-dop_complete)%>%
  distinct()

  head(lookup_dop)
  
```

#### Finally Generate your numerator

Generate your numerator according to your denominator just as we did above for lactation groups. 

Example code is shown in the chunk below.

 -  select the denominator
 
 -  assign time periods, lactation groups according to the denominator
 
 -  use a function to assign day of phase based on your lookup table



```{r, echo = TRUE}

mast_event_summary_dop<-read_parquet('data/intermediate_files/events_formatted.parquet')%>%
  
  #select event of interest
  filter(event %in% 'MAST')%>%  #select your disease or event
  
  #add the event counts the way you like
  fxn_add_event_counts()%>% 
  mutate(event_count_lact = case_when(
    event_count_lact <4~paste0('Mast ', event_count_lact), 
    TRUE~'Mast 4+'
  ))%>%
  
  #match the dates to the denominator (NOTE: this dop denominaor is by year rather than month)
  mutate(date_time_period_start = floor_date(date_event, unit = 'year'))%>% 
  
  #use same  lactation grouping as denominator (0, 1, 2, 3+), 
  #and set location to match denominator (locations will depend of farm data structure)
  mutate(`Lactation Group` = lact_group, 
         location_lact_list = location_event) %>% 
  
  
  
  #create_dop group
  fxn_assign_day_of_phase(lookup_tbl = lookup_dop)%>%

  #group by all variables in the denominator, plus any extras that you want (like event count), and summarize
  group_by(location_lact_list, `Lactation Group`, 
            date_time_period_start, event_count_lact, day_of_phase_group)%>% 
  summarize(ct_mast_events = n_distinct(id_animal))%>%
  ungroup()
  

```

###  Join denominator to numerator

```{r, echo = TRUE}
final_data_dop<-denominator_dop%>%
  rowid_to_column()%>%
  left_join(mast_event_summary_dop)%>%
  mutate(mast_rate = ct_mast_events/ct_animal_time_periods)

head(final_data_dop)
```

#### Look at results

```{r, echo = TRUE}

ggplot(final_data_dop%>%
         filter(event_count_lact %in% 'Mast 1'))+
  geom_point(aes(x = date_time_period_start, y= mast_rate, color = day_of_phase_group, fill = day_of_phase_group))+
    geom_smooth(aes(x = date_time_period_start, y= mast_rate, 
                    color = day_of_phase_group, group =  day_of_phase_group, 
                    fill = day_of_phase_group),alpha = .2 , span = .6)+

  facet_grid(location_lact_list~`Lactation Group`, scales = 'free')+
  labs(title = 'Mast 1')+
  theme_bw()



```

