---
title: "Sample Lameness Report"
editor: source
format: 
 html:
   embed-resources: true
   toc: true
   toc-location: left
execute:
    echo: false
    message: false
    warning: false
params:
  herd: 
  year: 2025
---

```{r}
library(tidyverse)
library(arrow)
library(dtplyr)
library(DT)
library(gt)
library(flextable)
library(gtsummary)

source('functions/fxn_dt_base.R') #functions to parse remarks and protocols

# load GC's lame functions
source('functions/fxn_load_os_fxns.R')
fxn_load_os_fxns()

animals <-read_parquet('data/intermediate_files/animals.parquet') 

events_formatted <- read_parquet('data/intermediate_files/events_formatted.parquet') |> 
     filter(event %in% c("LAME", "FOOTRIM")) 


date_max_pull <- max(events_formatted$date_event)
farm_name <- unique(events_formatted$location_event)


# denominator stuff
year_filter <- make_date(params$year, 1, 1)

deno_cal <- read_parquet(
  'data/intermediate_files/denominator_by_calendar_time_period.parquet') |> 
  filter(deno_type %in% c("lact_basic", "lact_5+") & 
           calendar_time_period_type == "year") |> 
  select(-c(contains("dop"), day_of_phase_group)) |> 
  filter(date_time_period_start >= year_filter & date_time_period_start < year_filter + years(1))

```


```{r}
#| label: summary data

summarize_events<-events_formatted |> 
  group_by(farm = location_event, event, protocols_remaining_after_numbers1, 
           remark_letters1
           ) |> 
  summarize(count_rows=sum(n()))|>
  ungroup()%>%
  mutate(event_type = factor(protocols_remaining_after_numbers1), 
         remark_type = factor(remark_letters1), 
         Event = factor(event),
         event_type = if_else(is.na(event_type),
                              "No Protocol Recorded", event_type),
         remark_type = if_else(is.na(remark_type), "No Remark Recorded",
                               remark_type)
         )

```

## Check out what Lesions are being reported

### Protocol Data

```{r}
#| fig-height: 12
# count y vars

facet_order <- summarize_events %>%
  group_by(farm, event_type) %>%
  summarise(n_y = n_distinct(event)) %>%
  arrange(desc(n_y)) %>%  # Order by most y categories
  pull(event_type)

# order events
summarize_events <- summarize_events %>%
  mutate(event_type = fct_reorder(event_type, count_rows, .fun = sum, .desc = FALSE)) 

  ggplot(summarize_events)+
  geom_bar(aes(x = event_type,
               y = count_rows, fill = event_type), stat = "identity")+
  #facet_wrap(factor(event, levels = facet_order) ~., scales = 'free')+
    facet_wrap(vars(farm, event), ncol = 2 , scales = "free")+
  coord_flip()+
  scale_fill_viridis_d()+
  theme_minimal()+
  labs(x = "",
       y = "Row Count")+
  theme(legend.position = "none",
        # axis.text.y = element_text(size = 6)
        )
```

### Remarks

Description of top 10 remarks recorded, Other is combined remaining remarks

```{r}
#| fig-height: 8

facet_order <- summarize_events %>%
  group_by(farm, remark_type) %>%
  summarise(n_y = n_distinct(event)) %>%
  arrange(desc(n_y)) %>%  # Order by most y categories
  pull(remark_type)

# order events
summarize_events <- summarize_events %>%
  # mutate(event_type = fct_reorder(remark_type, 
  #                                 count_rows, .fun = sum, .desc = FALSE)) 
  mutate(remark_type = fct_lump_n(remark_type,
                                 n = 10,
                                 ties.method = "random" ))
  

  ggplot(summarize_events)+
  geom_bar(aes(x = remark_type,
               y = count_rows, fill = remark_type), stat = "identity")+
  #facet_wrap(factor(event, levels = facet_order) ~., scales = 'free')+
    facet_wrap(vars(farm, event), ncol = 2, scales = "free")+
  coord_flip()+
  scale_fill_viridis_d()+
  theme_minimal()+
  labs(x = "",
       y = "Row Count")+
  theme(legend.position = "none",
        # axis.text.y = element_text(size = 6)
        )
  
```




```{r}
#| label: process_data

# assign lesion

# assign lesion variables 

all_lesions <- c("dd", "footrot", 'wld', "sole_ulcer","injury", 
                             "cork", "other", "hemorrhage",
                             "sole_fracture", "toe_ulcer", "thin",
                             "inf", "noninf", "toe", "axial", "lesion")

# for chroncity stuff
diseases <- c("inf", "noninf", "lesion")


lame_data <- events_formatted |> 
  select(id_animal, date_birth, date_fresh,lact_number, lact_group, 
         date_archived, date_event, event, 
         remark_letters1, protocols_letters1, location_event) |> 
  filter(event %in% c("LAME", "TRIM")) |>
  fxn_code_lesions(protocol_var = protocols_letters1,
                  remark_var = remark_letters1) |> 
  # fix ab and NA issues
  filter(!is.na(trimonly)) |>
  mutate(noninf = case_when(
    other == 1 & str_detect(protocols_letters1, "Ab") ~ 1,
    .default = noninf),
    # remove other catergory if abscess is found
    other = case_when(
      other == 1 & str_detect(protocols_letters1, "Ab") ~ 0,
      .default = other)
    ) |> 
  fxn_collapse_lesions(lesions = all_lesions) |> 
  fxn_trim_vars(location_event, id_animal,
                date_var = date_event,
                trimonly_var = trimonly) |> 
  fxn_dz_status(disease_cols = diseases,
                event_filter = trimonly == 0) |> 
# join with animals to get left date
  left_join(animals |> 
              select(id_animal, date_sold, date_died, date_left),
            by = "id_animal") |> 
# add cull data
  mutate(
    # create culling variables
    culled_ever = if_else(is.na(date_left), 0, 1),
    days_to_cull = date_left - date_event,
    # temp censor date need to adjust
    date_censor = ymd(date_max_pull) 
  ) |> 
  mutate(days_to_censor_cull = case_when(culled_ever == 1 ~
                                     days_to_cull,
                                    # cows not culled
                                    culled_ever == 0 ~
                                      date_censor - 
                                                    date_event,
                                    .default =  NA
                                    ),
    across(starts_with("days"), as.numeric)
    ) |> 
  group_by(location_event, id_animal) |> 
  mutate(culled_last_trim = 
           if_else(culled_ever == 1 & !is.na(days_to_next_trim), 0, 
                   culled_ever),
         culled_30 = if_else(culled_ever == 1 & 
                               days_to_cull <=30, 1, 0
                             )
         )|>
  ungroup() |> 
  select(location_event, id_animal, date_birth, lact_number, lact_group,
         date_event,
         date_left, date_died, date_sold,
         #lesion, inf, noninf,
         any_of(all_lesions),
         trimonly, times_trimmed, date_censor, 
         days_to_cull, days_to_censor_cull,culled_ever, culled_last_trim,
         culled_30, date_prev_trim, days_to_next_trim, 
         starts_with("life_"), starts_with("status_")
         )


```

```{r}
#| label: lesion-categories

# 1. Define which lesions fall into each category
infectious_lesions <- c("dd", "footrot")

non_infectious_lesions <- c(
  "wld", "sole_ulcer", "hemorrhage", 
  "sole_fracture", "toe_ulcer", 
  "thin", "cork", "injury")

  # labels for plot
  lesion_labels <- c(
    "dd"            = "Digital Dermatitis",
    "footrot"       = "Footrot",
    "wld"           = "White Line Disease",
    "sole_ulcer"    = "Sole Ulcer",
    "hemorrhage"    = "Hemorrhage",
    "sole_fracture" = "Sole Fracture",
    "toe_ulcer"     = "Toe Ulcer",
    "thin"          = "Thin Soles",
    "cork"          = "Corkscrew Claw",
    "injury"        = "Injury"
  )
  
all_lesions_label <- c(infectious_lesions, non_infectious_lesions)

```



```{r}
#| label: count lesions

inventory <- deno_cal |> 
  mutate(year = year(date_time_period_start)) |> 
  # pick just milking cows
  filter(`Lactation Group` == "LACT > 0") |>
  select(location_lact_list, year, ct_animal_time_periods, 
         'Lactation Group') |> 
  mutate(ct_animal_time_periods = round(ct_animal_time_periods, 0))
  

base_lesion_data <- lame_data |>
  mutate(year = year(date_event)) |>
    filter(year == params$year) |>
    pivot_longer(
    cols = all_of(all_lesions),
    names_to = "lesion_type",
    values_to = "has_lesion"
  ) |>
  filter(has_lesion == 1) |>
  mutate(
    lesion_group = if_else(lesion_type %in% infectious_lesions,
                           "Infectious Lesions", "Non-Infectious Lesions")
  ) |>
  count(location_event, year,
        lesion_group, lesion_type, status_lesion,
        name = "lesion_count") |>
  left_join(inventory, by = join_by(location_event == location_lact_list,
                                           year)) |> 
  mutate(incidence_rate = (lesion_count / ct_animal_time_periods) * 100
  ) 

# Create 2 specific data subsets
inf_data <- base_lesion_data |>
  filter(lesion_group == "Infectious Lesions")

noninf_data <- base_lesion_data |>
  filter(lesion_group == "Non-Infectious Lesions")


```


```{r}
#| label: graph function

plot_lollipop <- function(.data,
                          x_var = incidence_rate,
                          y_var = location_event, ...) {
  .data |>
    ggplot() +
    geom_segment(
      aes(
        x = {{ x_var }}, xend = 0,
        y = {{ y_var }}, yend = {{ y_var }},
        color = {{ y_var }}
      ),
      linewidth = 2
    ) +
    geom_point(
      aes(
        x = {{ x_var }}, y = {{ y_var }},
        color = {{ y_var }}
      ),
      size = 8
    ) +
    scale_color_viridis_d() +
    # adds some white space around edges so points not cut off
    scale_x_continuous(expand = expansion(mult = (c(.1, .1)))) +
    scale_y_discrete(expand = expansion(add = 1))
}


```

# Lesion Incidence
::: panel-tabset
## Summary Categories

```{r}
#| label: graph individual lesions

les_graph <- base_lesion_data |> 
  filter(lesion_type %in% c("lesion", "inf", "noninf", "other")
         ) |>
  mutate(lesion_type = fct_reorder(lesion_type, incidence_rate)
         )|>
  plot_lollipop(y_var = lesion_type)+
  geom_text(aes(x = incidence_rate, y = lesion_type,
                label = round(incidence_rate, 1)),
            nudge_x = +.01, color = "white", size = 3)+
  facet_grid(
    cols = vars(location_event),
    rows = vars(status_lesion),
  )+
  theme_minimal()+
  guides(color = "none")+
  labs(x = "Cases per 100 Cows", y = NULL)

les_graph

```

## Individual Lesions


```{r}
#| label: graph individual lesions

les_graph <- base_lesion_data |> 
  filter(lesion_type %in% (all_lesions_label)
         ) |>
  mutate(lesion_type = fct_reorder(lesion_type, incidence_rate)
         )|>
  plot_lollipop(y_var = lesion_type)+
  geom_text(aes(x = incidence_rate, y = lesion_type,
                label = round(incidence_rate, 1)),
            nudge_x = +.01, color = "white", size = 3)+
  facet_grid(
    cols = vars(location_event),
    rows = vars(status_lesion),
  )+
  theme_minimal()+
  guides(color = "none")+
  labs(x = "Cases per 100 Cows", y = NULL)

les_graph

```

:::

```{r}

# this counts overall lesions 
# count events
# 
# To then count all occurences diagnoses/events

last_year_floor <- floor_date(pull_date,"year")

lame_sum_all <- lame_events2 |> 
  filter(life_times_lame > 0) |> 
  select(-trimonly) |> 
  group_by(farm, floordate_year, lact_group_5) |> 
  summarize(across(all_of(all_lesions), \(x) sum(x, na.rm = TRUE)),
            .groups = "drop") |> 
  # Add totals by floordate_year
  bind_rows(
    lame_events2 |> 
      filter(life_times_lame > 0) |> 
      select(-trimonly) |> 
      group_by(farm, floordate_year) |> 
      summarize(across(all_of(all_lesions), \(x) sum(x, na.rm = TRUE))) |> 
      mutate(lact_group_5 = "LACT > 0")
  ) |>
  # filter out just last year
  filter(floordate_year == last_year_floor)  |> 
  pivot_longer(cols = all_of(all_lesions),
               names_to = "lesion_type",
               values_to = "count_all")


```

```{r}

# count incident events

# To then count first lesion occurrences.  Bases on 1st classification of any lesion in a cow's life. Could do by 1st for each lesion but harder to attribute cause to RF if skin/corium is damaged by lesion or compensation. For example if a cow gets DD and then an ulcer is the ulcer due to excessive standing time due to management or due to shifting weight to other leg due DD?

# this counts first lesions 

lame_sum_first <- lame_events2 |> 
  filter(life_times_lame == 1) |> 
  select(-trimonly) |> 
  # count lesions
  group_by(farm, floordate_year, lact_group_5)%>%
  summarize(across(all_of(all_lesions), \(x) sum(x, na.rm = TRUE)))%>%
  ungroup() |>
    # Add totals by floordate_year
  bind_rows(
    lame_events2 |> 
      filter(life_times_lame == 1 ) |> 
      select(-trimonly) |> 
      group_by(farm, floordate_year) |> 
      summarize(across(all_of(all_lesions), \(x) sum(x, na.rm = TRUE))) |> 
      mutate(lact_group_5 = "LACT > 0")
  ) |>
  # filter out just 2024
  filter(floordate_year == last_year_floor) |> 
  pivot_longer(cols = all_of(all_lesions),
               names_to = "lesion_type",
               values_to = "count_1st")

```

```{r}

# merge sum tables

lesion_table <- lame_sum_all |> 
  left_join(lame_sum_first, 
            by = join_by(farm, floordate_year, lact_group_5, lesion_type))

```

```{r}

# merge with denominators

# To turn this into a lacational risk and account for # cows we need to merge this with the denominators we calculated earlier
risk <- lesion_table |> 
    # filter out just 2024
  filter(floordate_year == last_year_floor & lact_group_5 != "Heifer") |> 
  left_join(herd_deno, by = join_by(farm, lact_group_5 == 'Lactation Group')) |> 
  mutate(risk_first = round(count_1st/count_lactations*100,1),
         risk_all = round(count_all/count_lactations * 100, 1),
         risk_first = if_else(is.na(risk_first), 0, risk_first),
         risk_all = if_else(is.na(risk_all), 0, risk_all)
         ) |> 
  select(-c(floordate_year))


```

## Table of lesion incidence

```{r}

lesion_labels <- c(
"Any Lesion" = "lesion",
  "Digital Dermatitis" = "dd",
  "Sole Ulcer" = "sole_ulcer",
  "White Line" = "wld",
  "Other" = "other",
  "Footrot" = "footrot",
  "Injury" = "injury",
  "Infectious" = "inf",
  "Non-Infectious" = "noninf",
  "Any Toe Lesion" = "toe",
  "Thin Sole" = "thin",
  "Toe Ulcer" = "toe_ulcer",
  "Hemorrhage" = "hemorrhage"
)

risk_gt <- risk |> 
  filter(lact_group_5 == "LACT > 0") |> 
  filter(risk_all>0) |> 
  select(farm, lesion_type, risk_first, risk_all) |> 
  arrange(desc(risk_first)) |> 
  mutate(lesion_type = as_factor(lesion_type)) |> 
  mutate(
    lesion_type = fct_recode(lesion_type, !!!lesion_labels)) |> 
  gt(groupname_col = "farm",
     row_group_as_column = TRUE) |> 
  tab_spanner(label = md("**% Risk for Case Type**"), columns = starts_with("risk")) |> 
  cols_label(lesion_type = "Lesion",
             risk_first = "1{{^st}}",
             risk_all = "All") |> 
    # tab_style(
    # style = cell_text(weight = "bold"),
    # locations = cells_column_spanners(everything())
    # ) |> 
  cols_align("right") |> 
  tab_footnote(footnote = "1st lifetime occurence of any lesion not of a particular lesion",
               locations = cells_column_labels(columns = risk_first)) |>
    tab_style(
    style = cell_text(align = "center", weight = "bold"),
    locations = cells_column_labels(everything())
    ) |> 
  cols_align(align = "center", columns = c(risk_first, risk_all))


risk_gt

```

```{r}
# code for graph (a dynamic function)

region_les_graph <- function(.data, 
                             facet_col = farm,
                             facet_row = time_period,
                             plot_var = lesion_type,
                             lesions = all_lesions,
                             years,
                             farms){
  # filter data
  df <- .data |> 
    filter(risk_all != 0) %>% 
    filter(time_period %in% years) |> 
    filter(lesion_type %in% lesions & farm %in% farms)
  
  # calculate min/max for graphs
  min <- df |> 
  mutate(min = min(risk_first, na.rm = TRUE)
         ) |> 
  slice_head() |>
  mutate((min = floor(min))) |> 
  select(min) 

min_limit <- min$min[1] 

max <- df |> 
  mutate(max = max(risk_all, na.rm = TRUE) 
         )|> 
  slice_head() |> 
  select(max) |> 
  mutate(max =ceiling(max)
  )
# extract max value
max_limit <- max$max[1]  

break_graph <- case_when(max_limit < 6 ~ 1,
                         max_limit > 6 & max_limit <11 ~ 2,
                         max_limit > 10 & max_limit < 51 ~ 5,
                         max_limit > 50 & max_limit < 101 ~ 10,
                         max_limit >101 ~ 20)

#graph
les_graph <- df %>%
#  group_by(farm, year) %>% 
  mutate(x_var = fct_reorder({{plot_var}}, risk_all)) %>% 
  ggplot() +
  geom_segment(aes(x = x_var, xend = x_var, 
                   y = risk_all, yend = risk_first, 
                   color = "Repeats"), 
               linewidth = 2) +
  geom_point(aes(x = x_var, y = risk_all, color = "All"), size = 6.5) +
  geom_text(aes(x_var, risk_all, label = round(risk_all, digits = 1)), 
            nudge_x = +.01, 
            color = "white", size = 2.25,
            show.legend = FALSE) +
  geom_point(aes(x = x_var, y = risk_first, color = "1st"), size = 6.5) +
  geom_text(aes(x_var, risk_first, label = round(risk_first, digits = 1)), 
            nudge_x = +.01,  
            color = "white", size = 2.25) +
  coord_flip() +
  theme_minimal() +
  xlab("") +
  ylab("# of cases per 100 cows") + 
  scale_y_continuous(limits = c(0, max_limit),
                     breaks = seq(0, max_limit, by = break_graph),
                     expand = c(0.02, 0.02)) +
  scale_x_discrete(expand = c(0.05, 0.05),
                   labels = lesion_labels) +
  scale_color_manual(name = "# of Cases", 
                     values = c("Repeats" = "#FDE725FF", #viridis colours
                                "All" = "#440154FF", 
                                "1st" = "#7ad151ff"),
                     labels = c("1st", "Repeats", "All"),
                     breaks = c("1st", "Repeats", "All")
  )+
  guides(color = guide_legend(override.aes = list(shape = c(19, NA, 19),
                                                  linetype = c(1, 1, 1)
  ),
  label.position = "bottom",
  title.position = "top",
  title.hjust = 0.5)
  )+
  theme(legend.position = "top")+
  facet_grid(cols = vars ({{facet_col}}), 
             rows = vars({{facet_row}}),
             labeller = labeller(lesion_type = lesion_labels))+
  theme(strip.text = element_text(face = "bold"))
}
```

## Graphical Lesion Distribution

```{r}
#| label: fig_any
#| fig-cap: "**A lot of repeat lesions**"
#| fig-cap-location: top
#| fig-height: 8


farms <- farm_name
years <- ("2025")
lesion_labels <- c(
  lesion = "Any Lesion",
  dd = "Digital Dermatitis",
  sole_ulcer = "Sole Ulcer",
  hemorrhage = "Hemorrhage",
  wld = "White Line",
  other = "Other",
  footrot = "Footrot",
  injury = "Injury",
  inf = "Infectious",
  noninf = "Non-Infectious",
  toe = "Any Toe Lesion",
  toe_ulcer = "Toe Ulcer",
  thin = "Thin Sole",
  cork = "Corkscrew"
)


graph_overall <- risk |> 
  filter(lact_group_5 == "LACT > 0") |> 
  region_les_graph(years = years, farms = farms)

graph_overall


```

## Graphical Lesion Distribution by Lactation Group

```{r}
#| fig-cap: "**More repeats in older cows**"
#| fig-cap-location: top
#| fig-height: 11

graph_lact <- risk |> 
  filter(lact_group_5 != "LACT > 0") |> 
  region_les_graph(years = years, farms = farms, facet_col = farm,
                   facet_row = lact_group_5)

graph_lact

```

```{r}
# set up for culling
# rough code needs to be improved

lame_cull <- lame_events2 |> 
  # for development 
  # select(site_id, primary_tag, date_trim, trimonly, date_cull) |> 
  # using dtplyr for speed but transfers var labels to new variables
  lazy_dt() |> 
  # deal with culling
  mutate(
    date_trim = date_event,
    # create culling variables
    culled_ever = if_else(is.na(date_left), 0, 1),
    days_to_cull = date_left - date_trim,
    # temp censor date need to adjust
    date_censor = ymd(pull_date) 
  ) |> 
  arrange(farm, id_animal, date_trim) |> 
  group_by(farm, id_animal) |> 
  # id prev trim date and time
  mutate(date_prev_trim = lag(date_trim, n = 1),
         days_from_prev_trim = date_trim - date_prev_trim,
         days_to_next_trim = lead(days_from_prev_trim, n =1),
         type_prev_trim = lag(trimonly, n = 1),
         type_next_trim = lead(trimonly, n = 1),
         # calc for lame cows time from last trim if last was a trim
         ## don't think need one below as can just use days from previous trim
         # days_from_trim = if_else(trimonly == 0 & type_prev_trim == 1,
         #                        date_trim - date_prev_trim, NA),
         ## don't need first one as only applies to trimonly to lame 
         # days_to_next_lame = lead(days_from_trim, n = 1),
         days_to_next_lame = if_else(type_next_trim == 0, 
                                     as.numeric(days_to_next_trim),
                                     NA_real_)
         ) |> 
  ungroup() |> 
  # set days to censor when trimmed again for time_to_event graphs
  # cows culled and not trimmed again
  mutate(
    days_to_censor_trim = case_when(is.na(days_to_next_trim) & culled_ever == 1 ~
                                     days_to_cull,
                                    # cows not culled or trimmed
                                    is.na(days_to_next_trim) & culled_ever == 0 ~
                                      date_censor - date_trim,
                                    # cows with next trimdate
                                    !is.na(days_to_next_trim) ~ 
                                      days_to_next_trim,
                                    .default =  as.difftime(NA, unit = "days")
                                    ),
    days_to_censor_cull = case_when(culled_ever == 1 ~
                                     days_to_cull,
                                    # cows not culled
                                    culled_ever == 0 ~
                                      date_censor - date_trim,
                                    .default =  as.difftime(NA, unit = "days")
                                    ),
         next_trim_lame = if_else(is.na(days_to_next_lame),0,1),
    across(starts_with("days"), as.numeric)
    ) |> 
  group_by(farm, id_animal) |> 
  mutate(culled_last_trim = 
           if_else(culled_ever == 1 & 
                     days_to_censor_trim != days_to_censor_cull, 0, 
                   culled_ever)
         )|>
  ungroup() |> 
  as_tibble()

```

## Time to cull after lesion diagnosis for Non infectious lesions

```{r}

source("functions/fxn_time_to_cull.R")

library(survival)
library(survminer)

life_colours <- c('Never any lesion' = "#440154ff" ,
                  'Once' = "#3b528bff",
                  'Twice' = "#21908cff",
                  '3 or more times' = "#fde725ff"
                  )


years <- "2025"

time_to_cull_non_inf <- lame_cull |>
  mutate(year = year(floordate_year)) |>
  survival_data(years = years,
                disease = noninf, life_x_dz = life_times_noninf)

km <- time_to_cull_non_inf |>
  km_fit(facet_col = farm, facet_row = year)

km

```

### Predicted culling risk at specific times for non-infectious lesions


```{r}
#| label: surv-table

# iterate over farms
# non infectious
non_inf_table <- map(farms, \(.x) km_fit_table(data = time_to_cull_non_inf,
                                     farms = .x)
           )

# label list
names(non_inf_table) <- farms

```

Tables with cumulative predicted % risk of cow being culled after a lesion occurence at specific time points.

:::: panel-tabset
```{r}
#| results: asis
#| label: non_inf_surv

# this creates tab for each farm

iwalk(non_inf_table, ~ {
  cat('## ', .y, '\n\n')
  
  # needed as a flextable
  cat(knitr::knit_print(.x), '\n\n')
  
})

```
::::


## Other graphing options

-   Time to repeat lesion

-   Time to lameness after a routine trim for healthy cows

-   Recheck compliance
