---
title: "Week 6 Milestone Template Report"
author: "Dakota Dairy Health"
date: "12.13.2025 /> <br> Other Name"  
format:
  html:
    logo: 
editor: visual
echo: false
embed-resources: true


---

```{r}
#| label: setup
#| include: false

#'/images/DDH.jpg'   # path to logo file

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse,
  dtplyr,
  gt,
  arrow,
  rmarkdown,
  lubridate,
  quarto, 
  arrow,
  zoo,
  forcats,
  purrr,
  stringr
  )

# data you will need for this report
events_formatted <- read_parquet(
  '../data/intermediate_files/events_formatted.parquet') 

# filter this data for LAME and TRIM in the event variable

#Logo doesn't go in the YAML 
#Chat GPT needs super specification to be useful- doesn't recognize .rmd vs .qmd, gotta say "in my .qmd file" 
```

```{=html}

<!-- The objective of this milestone is to start the creation of a
template you can use for reproducible reports going forward. Most of
this milestone will focus on customizing the look of the report that you
can use for future reports. We will also explore of the lameness data.We will use this template in future milestones.
A few notes:  
1) The logo contains a clickable link 
2) to use an image put it in the image folder (the one in the report is called 
  logo_no_background.png)
3)Any data (including farm name) that is reported in the text should use an inline text code chunk -->
```

Run this chuck below. It will open the example report in your browser.  You should delete this chunk in your final report

```{r}
#| label: open-html-r
#| eval: false

# 1. Define the file path
file_path <- "images/milestone_6.htm"

# 2. Open the browser
browseURL(file_path)
```


Objective

Explore recorded lameness/trim protocols

Use the protocols_letters1 variable to get the information about the
    lameness/trim protocols used.

```{r}

#| label: replicate_graph

  Trim_Protocol_Bar_Graph <- events_formatted %>%
  filter(event %in% c("LAME", "TRIM")) %>% 
  filter(
    !(event == "LAME" & protocols_letters1 == "Trim")  # remove Trim only for LAME
  ) %>% 
  # replace_na(list(protocols_letters1 = "NA")) %>% 
  filter(!is.na(event=="TRIM")) %>% 
  add_count(protocols_letters1, name = "trim_event_count") %>%  # add frequency column 
  filter( trim_event_count > 29) %>% 
  ggplot(aes(
    x = fct_rev(fct_infreq((protocols_letters1))),  # most frequent at top
    fill = protocols_letters1
  )) +
  coord_flip() +                        # horizontal bars
  geom_bar() +
  facet_wrap(~ event) +                  # facet by event
  scale_fill_viridis_d(na.value = "black") +
  labs(
    y = "Count of Events",
    x = "Lameness Protocols",
    fill = "Protocol"
  )
 Trim_Protocol_Bar_Graph
```

```{r}

#| label: count_by_remark
events_formatted %>% 
  filter(event %in% c("LAME", "TRIM")) %>% 
  # filter(!(event == "LAME" & protocols_letters1 == c("Penicillin", "H"))) %>% #Filtering out responses from Lame, Trim responses still present (2 Hs)
  count(remark, sort=TRUE)  #Ascending count 

```


NA exploration

```{r}

#| label: NA?

events_formatted_wide <- events_formatted %>%
  filter(event %in% c("LAME", "TRIM")) %>% 
  pivot_wider(
    names_from = event,
    values_from = remark)
#   ) %>% 
# filter(is.na(LAME) | is.na(TRIM)) 

str(events_formatted_wide)
nrow(events_formatted_wide)

na_table <- events_formatted_wide %>%
  summarize(
    na_lame = sum(is.na(LAME)),
    na_trim = sum(is.na(TRIM)),
    not_na_lame = sum(!is.na(LAME)),
    not_na_trim = 63300 - na_trim,  #total rows is 63300, wasn't working the other way 
    pct_na_trim = round((na_trim / (na_trim + not_na_trim)) * 100, 1),  
    pct_na_lame = round((na_lame / (na_lame + not_na_lame)) * 100, 1)
  )
print(na_table) #shows tibble, doesn't otherwise because of computed values I think  

# put your code to explore NA's here and name it na_lame_event so the code
# below will work
#na_lame_events <- na_explore(p)


# we will learn better ways to show tables later but for now this works
#rmarkdown::paged_table(na_lame_events)


 na_lame_events <- events_formatted %>% ## Is this looking for NAs by remark? 
  filter(event %in% c("LAME", "TRIM")) %>%
  filter(!is.na(remark)) %>%
  # replace_na(list(remark = "NA"))
  # filter(event == is.na(c("LAME", "TRIM"))) %>% 
  count(location_event, event, remark, name = "n") %>% 
  select(location_event, event, remark, n) %>% 
   arrange(desc(n))
 print(na_lame_events) 
```

Extension

For this week extension create a template for your future reports

-   customize the report to use your business' logo

-   use a theme/font colour scheme you prefer


```{r}
#| label: graphs
#| title: Lameness by Month

# events_formatted %>% 
#   distinct(event, pick(contains("LAME")))
# 
# 
# events_formatted %>%
#   filter(str_starts(event, "LAME")) %>%  # only events starting with "LAME"
#   count(event, sort=TRUE)

events_formatted_1 <-events_formatted %>% 
  mutate(floordate_month = floor_date(date_event, 'months'))%>%
    arrange(id_animal_lact, event, date_event)%>%
    group_by(id_animal_lact, event)%>%
    mutate(event_count = 1:n())%>%
    ungroup()%>%
    mutate(event = paste0(event, event_count)) 

lame_events <- c("LAME1", "LAME2", "LAME3", "LAME4", "LAME5", "LAME6", "LAME7", "LAME8","LAME9", "LAME10") #Use strings to filter longer things 


heat_data <- events_formatted_1 %>%
  mutate(floordate_date = floor_date(date_event, "month"),
         year = year(date_event)) %>% 
  filter(event %in% lame_events) %>%
  group_by(id_animal_lact) %>%
  mutate(
    date_lame = as.Date(date_event),
    num_lame = n()) %>%  # number of LAME events for this cow
    ungroup() 



events_formatted_1 <- events_formatted_1 %>% #Events_formatted not heat_data - second mutate for date_lame, different data set, different approach
  mutate(
    date_lame = if_else(
      str_starts(event, "LAME"),
      as.Date(date_event),
      as.Date(NA))) %>% 
    mutate(in_herd_6mo = if_else(
    any(floordate_month > (date_lame %m+% months(6)), na.rm = TRUE),
    "Yes",
    "No" )) 

events_formatted_1 <- events_formatted_1 %>% 
mutate(
    # date 6 months after first LAME
    lame_plus_6mo = date_lame %m+% months(6),
    # check if cow left the herd before 6 months
    in_herd_6mo = case_when(
      is.na(date_lame) ~ NA_character_,                     # no LAME event
      is.na(date_archived) ~ "Yes",                          # still in herd
      date_archived > lame_plus_6mo ~ "Yes",                # archived after 6 months
      date_archived <= lame_plus_6mo ~ "No"                 # archived before 6 months
    ) 
  )

heat_data <- events_formatted_1 %>% #Adding lame_plus_6mo to heat_data for heat map 
mutate(
    # date 6 months after first LAME
    lame_plus_6mo = date_lame %m+% months(6),
    # check if cow left the herd before 6 months
    in_herd_6mo = case_when(
      is.na(date_lame) ~ NA_character_,                     # no LAME event
      is.na(date_archived) ~ "Yes",                          # still in herd
      date_archived > lame_plus_6mo ~ "Yes",                # archived after 6 months
      date_archived <= lame_plus_6mo ~ "No"                 # archived before 6 months
    ) 
  )

##Checking my work 
heat_data %>% 
  count(in_herd_6mo, sort=TRUE)
```

```{r}
#| label: graphs2
#| title: Lameness by Month

# ##Heat Graph for Number Lame 
# heat_data %>% 
#   filter(year %in% c(2025,2024,2023), 
#          lact_group != "Heifer") %>% 
# ggplot(aes(x = floordate_month, y = lact_group_5, fill = num_lame)) +
#   geom_tile(color = "white") +                       # tiles for heat map
#   scale_fill_viridis_c(option = "C") +              # color gradient
#   labs(
#     x = "Month",
#     y = "Lactation Group",
#     fill = "Number of LAME Events",
#     title = "LAME Events Heat Map by Month and Lactation"
#   ) +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

# ##Heat Graph for Retention in Herd  -- Didn't really work - must run initial data chunk above first for the groups 
# heat_data %>% 
#   filter(year %in% c(2025,2024,2023), 
#          lact_group != "Heifer",
#          is.na(date_archived)) %>% 
# ggplot(aes(x = floordate_month, y = lact_group_5, fill = lame_plus_6mo)) +
#   geom_tile(color = "white") +                       # tiles for heat map
#   scale_fill_viridis_c(option = "C") +              # color gradient
#   labs(
#     x = "Month",
#     y = "Lactation Group",
#     fill = "Lame Plus 6 Months",
#     title = "LAME Events Heat Map by Month and Lactation"
#   ) +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

# #Bar Graph for Retention in Herd 
# heat_data %>% 
#   group_by(lact_group_5) %>% 
#   mutate(
#     lcount_by_lact = sum(num_lame)
#   ) %>% 
#   ungroup() %>% 
#   filter(year %in% c(2025,2024,2023), 
#          lact_group != "Heifer",
#          is.na(date_archived)) %>% 
#          # group_by(in_herd_6mo) %>% 
# ggplot(aes(x = year, y = lcount_by_lact, fill=lact_group_5)) +
#   geom_boxplot() +  
#   facet_wrap(vars(in_herd_6mo)) +
#   scale_fill_viridis_d()               
  
#Heat Graph including Herd Retention
heat_data %>%
  filter(year %in% c(2025),
         lact_group != "Heifer") %>%
  group_by(floordate_month, lact_group_5, in_herd_6mo) %>%
  summarise(lcount_by_lact = sum(num_lame, na.rm = TRUE) / n_distinct(id_animal_lact), .groups = "drop") %>%
  ggplot(aes(x = factor(floordate_month), y = lact_group_5, fill = lcount_by_lact)) +
  geom_tile(color = "white") +
  facet_wrap(~ in_herd_6mo) +
  scale_fill_viridis_c(option = "C") +
  labs(
    x = "Floordate_Month",
    y = "Lactation Group",
    fill = "Average Lame Event by Lactation",
    title = "LAME Events by Year, Lactation, and Herd Retention"
  ) +
  theme_minimal()

```



```

