---
title: "Milestone 5 - Denominators (Tidy and Join)"
format: html
date: "`r Sys.Date()`"
embed-resources: true
---

```{r}
library(tidyverse)
library(quarto)
library(arrow)
library(waldo)

solution<-read_rds('data_milestones/solutions_week_05_pivotlonger.rds')

```

## Denominators

Now that you can tidy data, pivot longer or wider, and then join tables to others, you are both unstoppable . . . and dangerous.

In this lesson we will explore one method of creating denominators.

The chunk below calls a script which will create a standard denominator file and save it in \`data/intermediate_files\` folder named `denominator_by_lact_group_time_periodXXX.parquet`.

The "XXX" in the file name represents the number of days within each time period used to denominator calculations.

When you run the chunk below it will - generate a denominator file with a time period of 365 days - read that file into your environment and name it deno365. (it will take a bit of time to run)

```{r initial denominator generation, message==FALSE}

quarto::quarto_render(
  input = "../step3_denominators_by_lactation_group.qmd",
  execute_dir = dirname("../step3_denominators_by_lactation_group.qmd"),
  execute_params = list(
    denominator_granularity = 365,
    cut_by_days = 30,
    top_cut = 400,
    top_cut_hfr = 500
  )
)

```

Run this code chunk to read in the denominator file you just created.

```{r}
deno365<-read_parquet('../data/intermediate_files/denominator_by_lact_group_time_period365.parquet')

```

## Part 1 - Explore lactation group denominators

There are multiple denominator types to choose from in this file. Write some code in the chunk below to list the names of the different values in the deno_type variable

```{r}
#| label: deno365 unique entries


deno365
unique(deno365[["Lactation Group"]])
unique(deno365[["deno_type"]])
```

You will notice that there are 2 basic types:

-   lactation groups (begin with "lact\_")
-   day of phase plus lactation group (begin with "dop\_")

In order to explore these options further, write some code in the chunk below that pivots the data so that you can graphically compare metric types more easily.

You should pivot the columns: "ct_animal_time_periods", "ct_animals" , "ct_animal_lactations" Name your new pivoted dataframe `deno365_long`. Name your new variables: `metric` and `ct`

Run this chunk to see an example of what your final table should look like

```{r}
head(solution)
```

```{r}
deno365_long <- deno365 %>%
  pivot_longer(
    cols = c(ct_animal_lactations, ct_animals, ct_animal_time_periods),
    names_to = "metric",
    values_to = "ct"
  )

# deno365_long <- deno365 %>% 
#   pivot_longer(
#     cols = starts_with("ct_"),
#     names_to = "metric",
#     values_to = "ct"
#   )

deno365_long

write_csv(solution,"excel_excuses.csv")
```

Run the chunk below to see if your solution matches

```{r}
waldo::compare(solution, deno365_long)

```

Part 2 - Compare denominators

Finding the right denominator is often more challenging than creating numerators.\
Run the chunk below to see a graphical comparison of the metrics available in deno_type `lact_basic`

```{r}
#### plot lact group counts

ggplot()+
  geom_point(data = deno365_long%>%filter(deno_type %in% 'lact_basic'),
             aes(x = date_time_period_start, y = ct, color = metric, fill = metric, shape = metric), 
             size = 3, alpha = .3, stroke = 2)+
  
  facet_grid(location_lact_list~`Lactation Group`, scales = 'free_y')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = 'top')+
  labs(fill = '', 
       color = '', 
       shape = '',
       title = 'Denominator Options')+
  scale_shape_manual(values = c(21,22,24,25))

```

In order to get more familiar with the denominator creation function you can read the markdown report in the reports folder and/or look at the code in the denominator `step3_denominators_by_lactation_group.qmd` file.

Modify the code below (***change the numeric values for the execute_params***) to create different time periods or day of phase cut points. Then describe the new denominator you generated using a graph, table or both.

```{r}

quarto::quarto_render(
  input = "../step3_denominators_by_lactation_group.qmd",
  execute_dir = dirname("../step3_denominators_by_lactation_group.qmd"),
  execute_params = list(
    denominator_granularity = 30, #modify this number to create time periods of different lengths (i.e. try  21 or 90 days)
      cut_by_days = 30, #this controls the number of days of phase (dim for cows, age for heifers) in each category.  A lower number will create more categories, a higher number will create fewer
      top_cut = 400, #What is the max DIM you care about? this puts a ceiling on the number of categories so when you have an outlier it doesn't give you too many groups
      top_cut_hfr = 500 #what is the max days of age you care about in heifers
    )
)

 
```

The new file you created can be found in the data/intermediate_files folder and will be named using the denominator_granularity that you set.

Here is a template to read in the new file you created.

You need to modify the "XXX" place holder so that it matches the number you put for denominator granularity in the chunk above.

```{r}
denoNEW<-read_parquet('../data/intermediate_files/denominator_by_lact_group_time_period30.parquet')
```

Use this code chunk to explore the new denominator

```{r}
#| label: denoNEW_long exploration
# =================================================================================
# denoNEW_long exploration
# =================================================================================

# pivot_longer the denoNEW(30day) framework
denoNEW_long <- denoNEW %>%
  pivot_longer(
    cols = c(ct_animal_lactations, ct_animals, ct_animal_time_periods),
    names_to = "metric",
    values_to = "ct"
  )

# write_csv(denoNEW_long,"excel_excuses.csv")

# visualize the new dataset, removing the 'Heifer' population from 'Lactation Group'

ggplot()+
  geom_point(data = deno365_long %>% filter(deno_type %in% 'lact_5+', `Lactation Group` != 'Heifer'), # 'lact_basic'
             aes(x = date_time_period_start, y = ct, color = metric, fill = metric, shape = metric), 
             size = 3, alpha = .3, stroke = 2)+
  
  facet_grid(location_lact_list~`Lactation Group`, scales = 'free_y')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = 'top')+
  labs(fill = '', 
       color = '', 
       shape = '',
       title = 'Denominator Options')+
  scale_shape_manual(values = c(21,22,24,25))


# =================================================================================
# Bar chart to indicate the number of individuals in each lactational group.
# =================================================================================

denoNEW_long %>%
  filter(
    deno_type == "dop_lact_5+",            # keep only 'dop_lact_5+'
    `Lactation Group` != "Heifer",         # exclude Heifer
    date_time_period_start >= 2025,        # only 2025 or later
    day_of_phase_group == "0 to 29",       # only the entry of the risk period 0 to 29
    metric == "ct_animals"                 # only ct_animals metric
  ) %>%
  ggplot(aes(x = `Lactation Group`, y = ct, fill = `Lactation Group`)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(
    x = "Lactation Group",
    y = "Count (ct)",
    title = "ct_animals by Lactation Group (lact_5+, 2025+)"
  )


# =================================================================================
# Bar chart to examine complete vs. incomplete entries by LGRP. 
# number of entries is the current plot
# =================================================================================

denoNEW_long %>%
  filter(
    deno_type == "dop_lact_5+",                # keep only lact_5+
    `Lactation Group` != "Heifer",         # exclude Heifer
    date_time_period_start >= 2025,         # only 2025 or later
    day_of_phase_group == "0 to 29",       # only the entry of the risk period 0 to 29
    metric == "ct_animals"                 # only ct_animals metric
    # !is.na(dop_complete)
  ) %>%
  ggplot(aes(x = `Lactation Group`, y = ct, fill = dop_complete)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top") +
  labs(
    x = "Lactation Group",
    y = "Count (ct)",
    fill = "DOP Completion",
    title = "ct_animals by Lactation Group (lact_5+, 2025+) split by DOP completion"
  )
```


```{r}
#| label: animals denominator parquet


event_form <- read_parquet('../data/intermediate_files/events_formatted.parquet')
animals

# =================================================================================

# animal_lact <- read_parquet('../data/intermediate_files/animal_lactations.parquet')
# animal_lact
# 
# unique(event_form[["event"]])  # what are the unique EVENT entries?
# 
# event_form %>%  # Enumerate the number of FRESH and MAST entries
#   filter(event %in% c("FRESH", "MAST")) %>%   # keep only FRESH and MAST
#   count(event)                                # count entries by event

# =================================================================================

library(dplyr)
library(lubridate)
library(ggplot2)

event_lact <- event_form %>%
  filter(lact_group_basic != "Heifer",
         event %in% c("FRESH", "MAST")) %>%
  mutate(
    floordate_date = floor_date(date_event, "month"),
    floordate_mo   = month(date_event, label = TRUE, abbr = FALSE)
  ) %>%
  arrange(id_animal, lact_number, event, date_event) %>%
  select(id_animal, breed, id_animal_lact, date_archived, lact_number,
         lact_group_basic, lact_group, lact_group_5, event_type, event,
         remark, protocols, Protocols, date_event, dim_event, locate_lesion,
         floordate_date, floordate_mo) %>%
  group_by(id_animal, lact_number) %>%
  mutate(
    SEQ = if_else(event == "FRESH", 1L, cumsum(event == "MAST"))
  ) %>%
  ungroup()

# Direct incidence calculation
incidence_summary <- event_lact %>%
  summarise(
    n_fresh   = sum(event == "FRESH"),
    n_mast_30 = sum(event == "MAST" & SEQ == 1 & dim_event <= 30),
    incidence_rate = n_mast_30 / n_fresh,
    incidence_pct  = incidence_rate * 100
  )


# =================================================================================
# Summarise MAST incidence by lact_group_5 and floordate_date
# =================================================================================

# incidence by lact_group_5 and month
incidence_summary <- event_lact %>%
  filter(floordate_date >= as.Date("2023-01-01")) %>%
  group_by(lact_group_5, floordate_date) %>%
  summarise(
    n_fresh   = sum(event == "FRESH"),
    n_mast_30 = sum(event == "MAST" & SEQ == 1 & dim_event <= 30),
    incidence_rate = n_mast_30 / n_fresh,
    incidence_pct  = incidence_rate * 100,
    .groups = "drop"
  )

# view the table
print(incidence_summary)

# Add year column for faceting
incidence_summary <- incidence_summary %>%
  mutate(year = year(floordate_date))

ggplot(incidence_summary, aes(x = floordate_date, y = lact_group_5, fill = incidence_pct)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(incidence_pct, 1)), 
            color = "black", 
            size = 3, 
            angle = 90, 
            vjust = 0.5, 
            hjust = 0.5) +
  scale_fill_gradient(low = "lightyellow", high = "red", name = "Incidence %") +
  facet_wrap(~ year, scales = "free_x") +   # facet by year, but keep floordate_date on x-axis
  scale_x_date(date_labels = "%b-%Y", date_breaks = "1 month") +  # show month-year labels
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank()
  ) +
  labs(
    x = "Month-Year",
    y = "Lactation Group",
    title = "Heatmap of Mastitis Incidence (first case ≤ 30 DIM)",
    subtitle = "Faceted by year, restricted to 2023+"
  )


# =================================================================================
# Summarise FRESH events by lact_group_5 and month
# =================================================================================

fresh_grid <- event_lact %>%
  filter(floordate_date >= as.Date("2023-01-01"),
         event == "FRESH") %>%
  group_by(lact_group_5, floordate_date) %>%
  summarise(
    n_fresh = n(), .groups = "drop"
  )

# View the grid table
print(fresh_grid)

# Plot as a grid heatmap or faceted bar chart
ggplot(fresh_grid, aes(x = floordate_date, y = n_fresh, fill = lact_group_5)) +
  geom_col(position = "dodge") +
  facet_grid(lact_group_5 ~ .) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "Month-Year",
    y = "Number of FRESH events",
    fill = "Lactation Group",
    title = "FRESH events by lactation group and month"
  )



# event_lact %>%
#   filter(event %in% c("FRESH", "MAST")) %>%   # keep only FRESH and MAST
#   count(event) 
# 
# names(event_lact)

# write_csv(event_lact,"excel_excuses.csv")

```

## Part 2 - Extension

Think about the data you described in milestone 4. Standard denominators like the one above are often not good enough.

Use your new data wrangling skills to create the perfect denominator for your questions about this data.

Options for creating denominators include:

1)  modify the code that creates your denoNEW to create time periods and or day of phase cut points that you want to use for your data in milestone 4.

2)  use your new join skills to join `animal_lactations.parquet` to `animals.parquet` and create your own denominator from scratch that improves your ability to answer a question about your data in milestone 4.

3)  Create a different denominator in a completely different way. (for some questions the best denominator is a subset of events pivoted wider)

NOTE: Denominators can be challenging. If you get stuck:

-   First articulate what you want to do, step by step, in English

-   Then add a blank code chunk for each step

-   Begin filling in code

-   Ask the group for help if you get completely stuck.
