---
title: "Week 6 Milestone Template Report"
format:
  html
embed-resources: true
---

```{r}
#| label: setup
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse,
  dtplyr,
  gt,
  arrow,
  rmarkdown,
  lubridate,
  quarto, 
  arrow,
  zoo
  )

# data you will need for this report
events_formatted <- read_parquet(
  '../data/intermediate_files/events_formatted.parquet')
animals <- read_parquet('../data/intermediate_files/animals.parquet')

# filter this data for LAME and TRIM in the event variable
lame_events <- events_formatted |> 
  filter(event %in% c("LAME", "TRIM"))


```

```{r}
#| label: Set date range:
pull_date <- unique(animals$data_pull_date_max)
date_start <- pull_date - 1825 # pulls last 5 years of data, modify for specific project
date_end <- pull_date
```

```{=html}

<!-- The objective of this milestone is to start the creation of a
template you can use for reproducible reports going forward. Most of
this milestone will focus on customizing the look of the report that you
can use for future reports. We will also explore of the lameness data.We will use this template in future milestones.
A few notes:  
1) The logo contains a clickable link 
2) to use an image put it in the image folder (the one in the report is called 
  logo_no_background.png)
3)Any data (including farm name) that is reported in the text should use an inline text code chunk -->
```

Run this chuck below. It will open the example report in your browser. You should delete this chunk in your final report

```{r}
#| label: open-html-r
#| eval: false

# 1. Define the file path
file_path <- "images/milestone_6.htm"

# 2. Open the browser
browseURL(file_path)
```

Objective

Explore recorded lameness/trim protocols

Use the protocols_letters1 variable to get the information about the lameness/trim protocols used.

```{r}
#| label: Lame over DIM
# put your graph code here

lame_data <- lame_events %>% 
  filter(is.na(date_archived)|date_archived > date_start) %>% 
  filter(dim_event >=0)

ggplot(lame_data, aes(x = dim_event)) +
  geom_histogram(binwidth = 10, fill = "steelblue", color = "black", alpha = 0.7) +
  theme_minimal(base_size = 14) +
  labs(
    title = "Distribution of Lameness Events Over Days in Milk",
    x = "Days in Milk",
    y = "Count"
  ) +
  theme(
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 14, face = "bold")
  )

```

```{r}
#| fig-height: 8
#| label: lame event types
summarize_lame_events<-lame_data |> 
  group_by(event, protocols_remaining_after_numbers1) |> 
  summarize(count_rows=sum(n()))|>
  ungroup()%>%
  mutate(event_type = factor(protocols_remaining_after_numbers1), 
         Event = factor(event),
         event_type = if_else(is.na(event_type), "Trim Only", event_type))

facet_order <- summarize_lame_events %>%
  group_by(event_type) %>%
  summarise(n_y = n_distinct(event)) %>%
  arrange(desc(n_y)) %>%  # Order by most y categories
  pull(event_type)

# order events
summarize_lame_events <- summarize_lame_events %>%
  mutate(event_type = fct_reorder(event_type, count_rows, .fun = sum, .desc = FALSE)) 

  ggplot(summarize_lame_events)+
  geom_bar(aes(x = event_type,
               y = count_rows, fill = event_type), stat = "identity")+
  #facet_wrap(factor(event, levels = facet_order) ~., scales = 'free')+
    facet_wrap(vars(event), ncol = 1, scales = "free")+
  coord_flip()+
  scale_fill_viridis_d()+
  theme_minimal()+
  labs(x = "",
       y = "Row Count")+
  theme(legend.position = "none",
        # axis.text.y = element_text(size = 6)
  )
```

```{r}
#| label: top 5 lame by dim
summarized_lame_events <- lame_data |> 
  group_by(dim_event, event, protocols_remaining_after_numbers1) |> 
  summarise(count_rows = n(), .groups = "drop") |> 
  mutate(event_type = factor(protocols_remaining_after_numbers1),
         event = factor(event),
         event_type = if_else(is.na(event_type), "Trim Only", event_type))

summarized_lame_events <- lame_data |> 
  mutate(
    dim_event = as.numeric(dim_event),
    dim_30 = floor(dim_event / 30) * 30
  ) |> 
  group_by(dim_30, event, protocols_remaining_after_numbers1) |> 
  summarise(count_rows = n(), .groups = "drop") |> 
  mutate(
    event_type = factor(protocols_remaining_after_numbers1),
    event = factor(event),
    event_type = if_else(is.na(event_type), "Trim Only", event_type)
  )

# Identify the top 5 most frequent event types
top_5_events <- summarized_lame_events |> 
  group_by(event_type) |> 
  summarise(total_count = sum(count_rows)) |> 
  arrange(desc(total_count)) |> 
  slice_head(n = 5) |> 
  pull(event_type)

# Filter dataset to include only top 5 event types
summarized_lame_events <- summarized_lame_events |> 
  filter(event_type %in% top_5_events)

# Plot stacked bar graph with 30-day tick marks on x-axis
ggplot(summarized_lame_events, aes(x = dim_30, y = count_rows, fill = event_type)) +
  geom_col(width = 14, position = "stack") +  # Use geom_col for numeric x-axis
  scale_fill_viridis_d() +  # Colorblind-friendly palette
  scale_x_continuous(breaks = seq(0, max(summarized_lame_events$dim_30), by = 90)) +  # Tick marks every 30 days
  theme_minimal(base_size = 14) +
  facet_wrap(vars(event_type), ncol = 3, scales = "free_y") +  # Separate facets for each event
  labs(
    title = "Stacked Bar Graph of Lameness Events by Days in Milk",
    x = "Days in Milk",
    y = "Count of Events",
    fill = "Event Type"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    panel.grid.major = element_line(color = "gray80", size = 0.3),  # Thinner grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    strip.text = element_text(size = 14, face = "bold"),
    legend.position = "right"
  )
```

```{r}
#| label: lame by month
monthly_lame_events <- lame_data |>
  mutate(
    date_event = as.Date(date_event),
    month = floor_date(date_event, "month")
  ) |>
  group_by(month, protocols_remaining_after_numbers1) |>
  summarise(count_rows = n(), .groups = "drop") |>
  mutate(
    event_type = if_else(
      is.na(protocols_remaining_after_numbers1),
      "Trim Only",
      as.character(protocols_remaining_after_numbers1)
    ),
    event_type = factor(event_type)
  )

top_5_monthly <- monthly_lame_events |>
  group_by(event_type) |>
  summarise(total_count = sum(count_rows), .groups = "drop") |>
  arrange(desc(total_count)) |>
  slice_head(n = 5) |>
  pull(event_type)

monthly_lame_events <- monthly_lame_events |>
  filter(event_type %in% top_5_monthly)

ggplot(monthly_lame_events, aes(x = month, y = count_rows, fill = event_type)) +
  geom_col() +
  scale_fill_viridis_d() +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Top 5 Lameness Events by Month",
    x = "Month",
    y = "Number of Events",
    fill = "Event Type"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right"
  )

```

NA exploration

```{r}
#| label: NA
# put your code to explore NA's here and name it na_lame_event so the code
# below will work
na_lame_events <- lame_events |> 
  count(is.na(remark), is.na(locate_lesion), is.na(date_event))

# we will learn better ways to show tables later but for now this works
rmarkdown::paged_table(na_lame_events)

```

Extension

For this week extension create a template for your future reports

-   customize the report to use your business' logo

-   use a theme/font colour scheme you prefer
