---
title: R Basics
format: html

#### The format can change- if you want a word doc change it to docx instead of html
#### There's a way to make it a google doc too - later 
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(arrow)
library(skimr)
library(waldo)
library(dplyr)
# We will learn what this code does in Milestone 2
animals <- read_parquet("../data/intermediate_files/animals.parquet")%>%
  filter(!(is.na(age_left)))

```

## R Basics

In this milestone, you'll become familiar with the `animals` data set.

## Recreation

### Part 1

The data we will use in our investigation is saved as an R object named `animals`. Use R to inspect the contents of `animals`:

-   Display the contents of `animals`
-   Use `nrow()` to find the number of observations in `animals`. Name this "number_of_rows". (hint: you should see "number_of_rows" in your environment)
-   Use `mean()` to find the average age an animal left (hint: use the variable named "age_left"). Name this "average_age_left".
-   Use `count()` from the dplyr package to count the number of observations associated with each location, breed and sex (hint: variable names should be "breed", "sex", "location_list". Name this 'counts'.

*Hint: you may want to look up the help pages for each of these functions.*

Write your code in the following chunk:

```{r}
#| label: recreation
#| 
nrow(animals)
number_of_rows <-nrow(animals)

mean(animals$age_left)
average_age_left <- (mean(animals$age_left))

animals %>% count(breed, sex, location_list)
counts <-animals %>% count(breed, sex, location_list)
## to make the pipe it's control, shift, "m" ->> %>% 
## This is useful when trying to keep your workflow nice, and the dplyr library is inside the tidyverse package 
## if you put a # in front of other variable it takes it out (in a list)
## and if you hit enter a lot it will respond differently if your syntax is correct or not 
```

#### Check your answers

To check your answers run the code chunks below. If your answer exactly matches the solution it will say "No differences". If you like your answer, but it is different we can discuss in class. There are many ways to do things that work.

Check number_of_rows:

```{r, echo=FALSE}

waldo::compare(number_of_rows, read_rds('data_milestones/solutions_week_01_number_of_rows.rds'))

```

Check age_left:

```{r, echo=FALSE}

waldo::compare(average_age_left, read_rds('data_milestones/solutions_week_01_age_left.rds'))

```

Check counts:

```{r, echo=FALSE}

waldo::compare(counts, read_rds('data_milestones/solutions_week_01_counts.rds'))

```

### Part 2

Now summarize the data:

-   Use `summary()` to generate a summary of the data set
-   Use `skim()` to see a different type of summary of the data set (warning: this function may take some time) - Bonus: save the output of your skim function to your environment. Name it "skim_animals".

Write your code in the following chunk:

```{r}
#| label: recreation of summary

summary(animals)

skim(animals)
skim_animals <-skim(animals)
```

Check your answer to `skim()`

```{r}
waldo::compare(skim_animals, read_rds('data_milestones/solutions_week_01_skim_animals.rds'))
```

## Extension

Explore `animals` in a new way. Consider using a new function, or something that you can learn from a help page. Alternatively, try to learn more about the other variables in `animals`. Keep in mind that we will study how to make plots for the next milestone.

Write your extension code in the following chunk:

```{r}
#| label: extension

min(animals$age_left)
max(animals$age_left)

mean_birth <-mean(animals$date_birth)
min_birth <-min(animals$date_birth)  
max_birth <-max(animals$date_birth)

birth_range <-(c(mean_birth, min_birth, max_birth))
birth_range
```
