---
title: "Milestone 5 - Denominators (Tidy and Join)"
format: html
date: "`r Sys.Date()`"
embed-resources: true
---

```{r}
#| warnings: false
#| message: false

library(tidyverse)
library(quarto)
library(arrow)
library(waldo)

solution<-read_rds('data_milestones/solutions_week_05_pivotlonger.rds')

#add some extra functions
source('data_milestones/fxn_floor_dates.R')

```

## Denominators

Now that you can tidy data, pivot longer or wider, and then join tables
to others, you are both unstoppable . . . and dangerous.

In this lesson we will explore one method of creating denominators.

The chunk below calls a script which will create a standard denominator
file and save it in \`data/intermediate_files\` folder named
`denominator_by_lact_group_time_periodXXX.parquet`.

The "XXX" in the file name represents the number of days within each
time period used to denominator calculations.

When you run the chunk below it will - generate a denominator file with
a time period of 365 days - read that file into your environment and
name it deno365. (it will take a bit of time to run)

```{r}
#| echo: false
#| message: false
#| include: false
#| warnings: false

quarto::quarto_render(
  input = "../step3_denominators_by_lactation_group.qmd",
  execute_dir = dirname("../step3_denominators_by_lactation_group.qmd"),
  execute_params = list(
    denominator_granularity = 365,
    cut_by_days = 30,
    top_cut = 400,
    top_cut_hfr = 500
  )
)

```

Run this code chunk to read in the denominator file you just created.

```{r}

deno365<-read_parquet('../data/intermediate_files/denominator_by_lact_group_time_period365.parquet')


```

## Part 1 - Explore lactation group denominators

There are multiple denominator types to choose from in this file. Write
some code in the chunk below to list the names of the different values
in the deno_type variable

```{r}

sort(unique(deno365$deno_type))

# graph optio to also show how hard it a wide is to graph
ggplot(deno365)+
  geom_col(aes(x = deno_type, y = ct_animals))



```

You will notice that there are 2 basic types:

-   lactation groups (begin with "lact\_")
-   day of phase plus lactation group (begin with "dop\_")

In order to explore these options further, write some code in the chunk
below that pivots the data so that you can graphically compare metric
types more easily.

You should pivot the columns: "ct_animal_time_periods", "ct_animals" ,
"ct_animal_lactations" Name your new pivoted dataframe `deno365_long`.
Name your new variables: `metric` and `ct`

Run this chunk to see an example of what your final table should look
like

```{r}
head(solution)
```

```{r}
#write your code to pivot the table here

deno365_long<-deno365%>%
  pivot_longer(cols = c('ct_animal_lactations', 'ct_animals', 'ct_animal_time_periods'), 
               names_to = 'metric', 
               values_to = 'ct' )

```

Run the chunk below to see if your solution matches

```{r}
waldo::compare(solution, deno365_long)

```

Part 2 - Compare denominators

Finding the right denominator is often more challenging than creating
numerators.\
Run the chunk below to see a graphical comparison of the metrics
available in deno_type `lact_basic`

```{r}
#### plot lact group counts

ggplot()+
  geom_point(data = deno365_long%>%filter(deno_type %in% 'lact_basic'),
             aes(x = date_time_period_start, y = ct, color = metric, fill = metric, shape = metric), 
             size = 3, alpha = .3, stroke = 2)+
  
  facet_grid(location_lact_list~`Lactation Group`, scales = 'free_y')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = 'top')+
  labs(fill = '', 
       color = '', 
       shape = '',
       title = 'Denominator Options')+
  scale_shape_manual(values = c(21,22,24,25))

```

In order to get more familiar with the denominator creation function you
can read the markdown report in the reports folder and/or look at the
code in the denominator `step3_denominators_by_lactation_group.qmd`
file.

Modify the code below (***change the numeric values for the
execute_params***) to create different time periods or day of phase cut
points. Then describe the new denominator you generated using a graph,
table or both.

```{r}
#| warning: false
#| include: false

quarto::quarto_render(
  input = "../step3_denominators_by_lactation_group.qmd",
  execute_dir = dirname("../step3_denominators_by_lactation_group.qmd"),
  execute_params = list(
    denominator_granularity = 30, #modify this number to create time periods of different lengths (i.e. try  21 or 90 days)
      cut_by_days = 60, #this controls the number of days of phase (dim for cows, age for heifers) in each category.  A lower number will create more categories, a higher number will create fewer
      top_cut = 400, #What is the max DIM you care about? this puts a ceiling on the number of categories so when you have an outlier it doesn't give you too many groups
      top_cut_hfr = 500 #what is the max days of age you care about in heifers
    )
)

 
```

The new file you created can be found in the data/intermediate_files
folder and will be named using the denominator_granularity that you set.

Here is a template to read in the new file you created.

You need to modify the "XXX" place holder so that it matches the number
you put for denominator granularity in the chunk above.

```{r}

denoNEW<-read_parquet('../data/intermediate_files/denominator_by_lact_group_time_period30.parquet')

```

Use this code chunk to explore the new denominator

Trying to get month \#'s so can see seasonal trends and figure out
complete vs incomplete

```{r}
# get seasonal numbers for last year
deno365_long_new <- denoNEW %>%
  filter(deno_type %in% c('lact_3+', 'dop_lact_3+')) %>%
  filter(date_time_period_start >= '2024-09-01' & 
           date_time_period_end <= '2025-10-05') %>%
  pivot_longer(cols = c('ct_animal_lactations', 'ct_animals',
                        'ct_animal_time_periods'), 
               names_to = 'metric',
               values_to = 'count' )
```

show levels fo day_of_phase_group to be able to use as a factor

```{r}
# test levels

sort(unique(deno365_long_new$day_of_phase_group))
```

```{r}
# graphs

dim_levels <- c("-Inf to 0","0 to 59", "60 to 119",
                "120 to 179", "180 to 239",
                "240 to 299", "300 to 359",
                "360 to Inf") 

graph_data <- deno365_long_new |> 
  rename(lact_group = 'Lactation Group') |>
  filter(str_detect(lact_group, "LACT")) |> 
  # adds total
  group_by(date_time_period_start,
           lact_group,
           metric) |>
  mutate(total = sum(count, na.rm = TRUE) ) |> 
  ungroup() |> 
  mutate(month_year = floor_date(date_time_period_start, "month"),
         day_of_phase_group = fct_relevel(factor(day_of_phase_group, 
                                                levels = dim_levels)
                                          ),
         metric = fct_recode(factor(metric),
                              'Lactations' =  'ct_animal_lactations',
                              'Animals' = 'ct_animals',
                             'Animal Time' = 'ct_animal_time_periods')
  ) |> 
  mutate(
         metric = fct_relevel(metric, "Animals", "Lactations", 
                              "Animal Time")
                                ) 

graph_data_totals <- graph_data |> 
  filter(!day_of_phase_group == "NA to NA") |>
  select(month_year,
         lact_group,
         metric,
         total) |> 
  distinct() |> 
  mutate(total = round(total,0))
```

Graph comparing denominators

-   For lact 1 and 2 numbers for animals and lactations are the same as
    cows calving end up in next lact level

    -   This in not true for lact 3+ hence lactation and animal \#'s
        differ

-   Animal time accounts for time at risk and hence is lower as some
    cows only spend part of the time in each time period. (formula is
    total animal time in TP/# of days in TP

```{r}
graph <- graph_data |>
#  filter(metric %in% ("ct_animals")) |>
  filter(!day_of_phase_group == "NA to NA") |>
  ggplot()+
  geom_col(aes(x = month_year,
                 y = count,
                 fill = fct_rev(day_of_phase_group),
               #shape = metric
               ),
           # this add white between each category to make it cleaner
           color = "white"
             #size = 3, alpha = .3, stroke = 2
             )+
  geom_text(data = graph_data_totals, 
            aes(x = month_year,
                    y = total,
                    label = total),
                hjust = 1.5,
                size = 2,
                color = 'black'
                )+
  coord_flip()+
  facet_grid(cols = vars(lact_group),
             rows = vars(metric),
              scales = "free_y")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = 'top',
        legend.title.position = "top",
        legend.text = element_text(size = 8),
        legend.key.size = unit(.25, "cm")
        )+
  guides(fill = guide_legend(nrow = 1,
         reverse = TRUE)
         )+
  labs(fill = 'DIM Categories',
       y = 'Count of Animals',
       x = 'Month',
       color = '',
       shape = '',
       title = 'Denominator Options')+
  scale_fill_viridis_d()


graph

```

## Part 2 - Extension

Think about the data you described in milestone 4. Standard denominators
like the one above are often not good enough.

Use your new data wrangling skills to create the perfect denominator for
your questions about this data.

Options for creating denominators include:

1)  modify the code that creates your denoNEW to create time periods and
    or day of phase cut points that you want to use for your data in
    milestone 4.

2)  use your new join skills to join `animal_lactations.parquet` to
    `animals.parquet` and create your own denominator from scratch that
    improves your ability to answer a question about your data in
    milestone 4.

3)  Create a different denominator in a completely different way. (for
    some questions the best denominator is a subset of events pivoted
    wider)

NOTE: Denominators can be challenging. If you get stuck:

-   First articulate what you want to do, step by step, in English

-   Then add a blank code chunk for each step

-   Begin filling in code

-   Ask the group for help if you get completely stuck.

# Incidence of Lameness per month using code from milestone 2

```{r}

# extension data

events_formatted <- read_parquet('../data/intermediate_files/events_formatted.parquet') %>%
  add_new_variables()

extension <- events_formatted %>%
  filter(event == "LAME1") |> 
  filter(date_event > max(date_event) - 
          lubridate::years(1)
         ) %>%
  group_by(location_event, protocols) %>%
  count(name = "n_lame_protocols"
  ) %>%
  ungroup() |> 
  arrange(desc(n_lame_protocols))

```

```{r}

# then extract dim of top 4 protocols with most lame events

dim_lame <- events_formatted %>%
  filter(event == "LAME1", lact_group != "Heifer") |> 
  filter(date_event > max(date_event) - 
           lubridate::years(1)
  ) %>%
  filter(protocols %in% extension$protocols[1:4]) %>%
  # calculate DIM windows
  mutate(dim_cat = round(dim_event/60, 0),
         dim_cat = if_else(dim_event>359, 6, dim_cat),
         dim_cat = (factor(dim_cat)),
         dim_cat = fct_recode(dim_cat,
                              "<-Inf to 0" = "-1",
                              "0 to 59" = "0",
                              "60 to 119" = "1",
                              "120 to 179" = "2",
                              "180 to 239" = "3",
                              "240 to 299" = "4",
                              "300 to 359" = "5",
                              "360 to Inf" = "6")
         ) |> 
  # select variables and rename OTF
  select(location_event, id_animal, month_year = floordate_month ,
         lact_group, protocols, dim_event, date_event, dim_cat
         ) |> 
  # now get counts by lesion and dim category
  group_by(location_event,month_year, 
           lact_group, protocols, dim_cat) %>%
  summarise(count_event = n(),
            .groups = "drop"
            ) 

```

```{r}
# join 2 data set

risk_data <- graph_data |> 
  filter(!day_of_phase_group == "NA to NA") |>
  filter(metric == "Animals" ) |> 
  rename(dim_cat = day_of_phase_group) |> 
  left_join(dim_lame, by = join_by(location_lact_list == location_event,
                                   lact_group, 
                                   month_year, dim_cat)) |> 
  # replace NA in count_event with 0 to allow calculations
  mutate(count_event = if_else(is.na(count_event), 0, count_event),
         risk = round(count_event/count * 100,1)
         )

```

# Most common lesion is Digital dermatitis and likely found at the time of routine trimming at dry-off and mid lactation. Some of evidence of heat stress impact on lesion occurence
```{r}
# graph occurence data

#| label: fig-lesion
#| fig-cap: "Older cows have more lesion"

graph <- risk_data |> 
  filter(!is.na(protocols)) |> 
  filter(lact_group == "LACT 3+") |> 
  mutate(protocols = fct_reorder(protocols, risk)) |> 
  ggplot()+
  geom_segment(aes(x = month_year, xend = month_year, 
                   y = risk, yend = 0, 
                   color = factor(month_year)), 
               linewidth = 2)+
  geom_point(aes(x = month_year, y = risk, 
                 color = factor(month_year)), 
             size = 6) +
  geom_text(aes(month_year, 
                risk, label = round(risk, digits = 1)), 
            nudge_x = +.01, 
            color = "white", size = 2.5,
            show.legend = FALSE)+ 
  facet_grid(cols = vars(dim_cat),
             rows = vars(protocols),
              scales = "free_y")+
  theme(strip.text = element_text(face = "bold"))+
  coord_flip() +
  theme_minimal() +
  # gets rid of legend
  theme(legend.position = "",
        plot.title = element_text(hjust = 0.5, face = "bold", size = 12))+
  labs (title = "DIM Categories",
        x = "",
        y = "Monthly # of cases per 100 cows"
        ) +
  # pretty colours 
  scale_x_date(date_breaks = "2 month", date_labels = "%b %Y") +
  scale_color_viridis_d()

graph


```


