---
title: "Milestone Week-6 Template"
author: "Kirkpatrick & Son Dairy Data"
date: "13 December 2025"

format:
  html:
    logo: logo_b.png   # path to logo file
editor: visual
echo: false
---

# Health Reporting Template

DC305 EVENTS data has been extracted. This report focuses on the EVENTS of LAME and TRIM.



```{r}
#| label: setup
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse,
  dtplyr,
  gt,
  arrow,
  rmarkdown,
  lubridate,
  quarto, 
  arrow,
  zoo,
  gghalves,   # needed for half violin plots
  )

# data you will need for this report
events_formatted <- read_parquet(
  '../data/intermediate_files/events_formatted.parquet')
```

### Data processing and preparation script

```{r echo=TRUE}
#| label: Extract LAME and TRIM
#| 
lame_trim <- events_formatted %>%
  # Filter for relevant events
  filter(lact_group_basic != "Heifer",
         event %in% c("LAME", "TRIM")) %>%
  # Sort before cumulative count
  arrange(id_animal, lact_number, event, date_event) %>%
  # Group by animal, lactation, and event
  group_by(id_animal, lact_number, event) %>%
  mutate(
    year_event = year(date_event),
    floordate_date = floor_date(date_event, "month"),
    floordate_month = month(date_event, label = TRUE, abbr = FALSE),
    locate_qtr = case_when(
      nchar(locate_lesion) == 8 ~ "ALL",
      nchar(locate_lesion) == 6 ~ "3Q",
      nchar(locate_lesion) == 4 ~ "2Q",
      nchar(locate_lesion) == 2 ~ locate_lesion,
      TRUE ~ NA_character_
    ),
    # cumulative case count per group
    SEQ = row_number()
  ) %>%
  ungroup()

# unique(lame_trim$lact_group_5)

corrections <- c(     #Correct the multiple entries to group pathology
  "Trim Only" = "Trim Only",
  "Ulcer/Block" = "Ulcer",
  "Abscess" = "Abscess",
  "Abces\\Block" = "Abscess",
  "Ulcer" = "Ulcer",
  "Absce/BlkPoly" = "Abscess",
  "Thin Sole" = "Thin Sole",
  "Injury" = "Injury",
  "Injury/Excede" = "Injury",
  "Injury/Poly" = "Injury",
  "Injury/Block" = "Injury",
  "Ulcer/BlkExce" = "Ulcer",
  "Ulcer/BlkPoly" = "Ulcer",
  "Remove Block" = "Remove Block",
  "Foot Rot/Exce" = "Foot Rot",
  "Foot Rot" = "Foot Rot",
  "FootRot/Poly" = "Foot Rot",
  "Absc/BlkExced" = "Abscess",
  "TR Lame Infec" = "TR Lame Infec",
  "Hairy Wart" = "Hairy Wart"
)

lame_trim <- lame_trim %>%
  mutate(protocols_numbers1 = recode(Protocols, !!!corrections))
```

## LAME Evaluation


### What are the historical (ALL) case counts by LGRP(3+)?

```{r}
#| label: Bar Graph LGRP case counts
#| 


# Ensure lact_group_5 has the correct order
lame_trim$lact_group_5 <- factor(
  lame_trim$lact_group_5,
  levels = c("LACT 1", "LACT 2", "LACT 3", "LACT 4", "LACT 5+")
)

# ==============================================================================
# Vertical bar graphs to indicate case count by calendar month
# ==============================================================================

lame_trim %>%
  filter(event == "LAME",
         year(floordate_date) >= 2023) %>%   # filter from 2023 to current
  ggplot(aes(x = floordate_date, fill = lact_group)) +
  geom_bar(color = "black") +
  labs(
    x = "Month/Year",
    y = "Case Count",
    title = "LAME Case Counts by Month/Year",
    caption = "All cases by calendar date",
    fill = "Lactation Group"
  ) +
  facet_wrap(~ lact_group, ncol = 1, scales = "fixed") +  # vertical panels, shared y-axis
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

### What is the distribution of ALL LAME cases?

```{r}
#| label: ALL Cases Half Violin and Boxplot

# ==============================================================================
# Coplot of half violin and boxplot for ALL LAME cases - scale = count
# ==============================================================================

lame_trim %>%
  filter(event == "LAME",
         lact_group != "Heifer", year(floordate_date) >= 2023) %>%   # filter only LAME events
  ggplot(aes(x = factor(year_event), y = dim_event)) +
  geom_boxplot(width = 0.3, outlier.shape = NA) +   # boxplot
  geom_half_violin(side = "l", fill = "orange", alpha = 0.6, scale = "count") +  # half violin on left
  labs(
    x = "Year of Event",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ LAME Event by Year",
    caption = "Representation by COUNT (ALL cases)"
  ) +
    scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### What is the distribution of FIRST LAME cases?

```{r}
#| label: FIRST Cases Half Violin and Boxplot

# ==============================================================================
# Coplot of half violin and boxplot for FIRST LAME cases - scale = count
# ==============================================================================

lame_trim %>%
  filter(event == "LAME",
         lact_group != "Heifer", year(floordate_date) >= 2023, SEQ == 1) %>%   # filter only LAME events
  ggplot(aes(x = factor(year_event), y = dim_event)) +
  geom_boxplot(width = 0.3, outlier.shape = NA) +   # boxplot
  geom_half_violin(side = "l", fill = "orange", alpha = 0.6, scale = "count") +  # half violin on left
  labs(
    x = "Year of Event",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ LAME Event by Year",
    caption = "Representation by COUNT, (1st cases)"
  ) +
    scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### By LGRP, what is the distribution of FIRST LAME cases?

```{r}
#| label: LGRP 1st Cases Half Violin and Boxplot
#| 

# ==============================================================================
# Coplot of half violin and boxplot for 1st LAME cases, 2024 + 2025, by LGRP - scale = count
# ==============================================================================

my_fills <- c(
  "LACT 1" = "lightblue",
  "LACT 2" = "lightgreen",
  "LACT 3+" = "tomato"
)

lame_trim %>%
  filter(event == "LAME",
         lact_group != "Heifer",
         SEQ == 1,
         year_event %in% c(2024, 2025)) %>% 
  ggplot(aes(x = lact_group, y = dim_event, fill = lact_group)) +
  geom_boxplot(width = 0.3, outlier.shape = NA, alpha = 0.6) +   # boxplot parameters
  geom_half_violin(side = "l", scale = "count") +  # half violin on left
  labs(
    x = "1st LAME, LGRP demographics (2024-2025)",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ LAME Event by Lactation Group",
    caption = "Representation by LGRP, 1st cases & COUNT"
  ) +
  scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  scale_fill_manual(values = my_fills) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### By LGRP what is the distribution of ALL LAME cases?

```{r}
#| label: LGRP ALL Cases Half Violin and Boxplot
#| 

# ==============================================================================
# Coplot of half violin and boxplot for ALL LAME cases, 2024 + 2025, by LGRP - scale = count
# ==============================================================================

my_fills <- c(
  "LACT 1" = "lightblue",
  "LACT 2" = "lightgreen",
  "LACT 3+" = "tomato"
)

lame_trim %>%
  filter(event == "LAME",
         lact_group != "Heifer",
         year_event %in% c(2024, 2025)) %>% 
  ggplot(aes(x = lact_group, y = dim_event, fill = lact_group)) +
  geom_boxplot(width = 0.3, outlier.shape = NA, alpha = 0.6) +   # boxplot parameters
  geom_half_violin(side = "l", scale = "count") +  # half violin on left
  labs(
    x = "ALL LAME, LGRP demographics (2024-2025)",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ LAME Event by Lactation Group",
    caption = "Representation by LGRP, ALL cases & COUNT"
  ) +
  scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  scale_fill_manual(values = my_fills) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### By LGRP, per treated cow what is the average case count?

```{r}
#| label: Average number of Lame Cases
#| 

# ==============================================================================
# Plot of average number of treatments by LGRP(3+) and year
# ==============================================================================


# Define custom fills
my_fills <- c(
  "LACT 1" = "lightblue",
  "LACT 2" = "lightgreen",
  "LACT 3+" = "tomato"
)

# Prepare the summarized data
lame_summary <- lame_trim %>%
  filter(event == "LAME",
         year_event %in% c(2023, 2024, 2025)) %>%
  group_by(year_event, lact_group) %>%
  # Summarize the SEQ column for LAME cases
  summarise(
    mean_SEQ = mean(SEQ, na.rm = TRUE),
    sd_SEQ   = sd(SEQ, na.rm = TRUE),
    n        = n(),
    .groups  = "drop"
  ) %>%
  # Determine an 80% confidence interval
  mutate(
    se = sd_SEQ / sqrt(n),
    # 80% confidence interval uses z ≈ 1.28
    ci = 1.28 * se
  )

# Plot with black borders and mean labels
ggplot(lame_summary, aes(x = factor(year_event),
                         y = mean_SEQ,
                         fill = lact_group)) +
  geom_col(position = position_dodge(width = 0.9),
           colour = "black") +
  geom_errorbar(aes(ymin = mean_SEQ - ci,
                    ymax = mean_SEQ + ci),
                width = 0.2,
                position = position_dodge(width = 0.9)) +
  geom_text(aes(label = round(mean_SEQ, 2)),   # display mean values
            position = position_dodge(width = 0.9),
            vjust = -1.2, size = 3.5) +        # adjust vertical placement
  scale_fill_manual(values = my_fills) +
  labs(
    x = "Year",
    y = "Average number of LAME cases (SEQ)",
    fill = "Lactation Group",
    title = "Average LAME Cases by Year and Lactation Group (2023–2025)",
    caption = "Average cases per treated cow"
  ) +
  theme_minimal()
```

### What are the historical identified LAME lesions (ALL)?

```{r}
#| label: LAME identification ALL treatments
#| 

# ==============================================================================
# Stacked bar graph of recorded treatment protocols - ALL treatments
# ==============================================================================

lame_trim %>%
  filter(event == "LAME", 
         year_event %in% c(2024, 2025)) %>% 
  ggplot(aes(x = floordate_date, fill = protocols_numbers1)) +
  geom_bar(color = "black") +   # adds black border around each stacked cell
  labs(
    x = "Month/Year", 
    y = "Number of Treatments",
    title = "Treatment Protocols by Month/Year",
    caption = "Representation by Time Interval, ALL cases"
  ) +
    scale_y_continuous(
    limits = c(0, 180), 
    breaks = seq(0, 180, by = 20),
    labels = paste0(seq(0, 180, by = 20), "")
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  ) +
  scale_fill_brewer(palette = "BrBG")       # references the 9-class ColorBrewer BrBG palette
```

### What are the historical identified LAME lesions (FIRST)?

```{r}
#| label: LAME identification FIRST treatments
#| 

# ==============================================================================
# Stacked bar graph of recorded treatment protocols - 1st treatments
# ==============================================================================

lame_trim %>%
  filter(event == "LAME", 
         year_event %in% c(2024, 2025), SEQ == 1) %>% 
  ggplot(aes(x = floordate_date, fill = protocols_numbers1)) +
  geom_bar(color = "black") +   # adds black border around each stacked cell
  labs(
    x = "Month/Year", 
    y = "Number of Treatments",
    title = "Treatment Protocols by Month/Year",
    caption = "Representation by Calendar Date, 1st cases"
  ) +
    scale_y_continuous(
    limits = c(0, 180), 
    breaks = seq(0, 180, by = 20),
    labels = paste0(seq(0, 180, by = 20), "")
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  ) +
  scale_fill_brewer(palette = "BrBG")       # references the 9-class ColorBrewer BrBG palette
```

### What are the historical identified LAME LIMBS (ALL)?

```{r}
#| label: LIMB assignments ALL treatments
#| 

# ==============================================================================
# Stacked bar graph of recorded QTR = FOOT Assignment - ALL treatments
# ==============================================================================

lame_trim %>%
  filter(event == "LAME", 
         year_event %in% c(2024, 2025)) %>% 
  ggplot(aes(x = floordate_date, fill = locate_qtr)) +
  geom_bar(color = "black") +   # adds black border around each stacked cell
  labs(
    x = "Month/Year", 
    y = "Number of Treatments",
    title = "Treatment Limbs by Month/Year",
    caption = "Representation by Calendar Date, ALL cases"
  ) +
    scale_y_continuous(
    limits = c(0, 180), 
    breaks = seq(0, 180, by = 20),
    labels = paste0(seq(0, 180, by = 20), "")
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  ) +
  scale_fill_brewer(palette = "BrBG")       # references the 9-class ColorBrewer BrBG palette

```

## TRIM Evaluation

### What are the historical (ALL) case counts by LGRP(3+)?

```{r}
#| label: Graph TRIM case counts by LGRP
#| 


# Ensure lact_group_5 has the correct order
lame_trim$lact_group_5 <- factor(
  lame_trim$lact_group_5,
  levels = c("LACT 1", "LACT 2", "LACT 3", "LACT 4", "LACT 5+")
)

# ==============================================================================
# Vertical bar graphs to indicate case count by calendar month
# ==============================================================================

lame_trim %>%
  filter(event == "TRIM",
         year(floordate_date) >= 2023) %>%   # filter from 2023 to current
  ggplot(aes(x = floordate_date, fill = lact_group)) +
  geom_bar(color = "black") +
  labs(
    x = "Month/Year",
    y = "Case Count",
    title = "TRIM Case Counts by Month/Year",
    caption = "All cases by calendar date",
    fill = "Lactation Group"
  ) +
  facet_wrap(~ lact_group, ncol = 1, scales = "fixed") +  # vertical panels, shared y-axis
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

### What is the distribution of ALL TRIM cases?

```{r}
#| label: Distribution of ALL TRIM case counts
#| 

# ==============================================================================
# Coplot of half violin and boxplot for ALL TRIM cases - scale = count
# ==============================================================================

lame_trim %>%
  filter(event == "TRIM",
         lact_group != "Heifer", year(floordate_date) >= 2023) %>%   # filter only TRIM events
  ggplot(aes(x = factor(year_event), y = dim_event)) +
  geom_boxplot(width = 0.3, outlier.shape = NA) +   # boxplot
  geom_half_violin(side = "l", fill = "lightgreen", alpha = 0.6, scale = "count") +  # half violin on left
  labs(
    x = "Year of Event",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ TRIM Event by Year",
    caption = "Representation by COUNT (ALL cases)"
  ) +
    scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### What is the distribution of FIRST TRIM cases?

```{r}
#| label: Distribution of FIRST TRIM case counts
#| 

# ==============================================================================
# Coplot of half violin and boxplot for FIRST TRIM cases - scale = count
# ==============================================================================

lame_trim %>%
  filter(event == "TRIM",
         lact_group != "Heifer", year(floordate_date) >= 2023, SEQ == 1) %>%   # filter only LAME events
  ggplot(aes(x = factor(year_event), y = dim_event)) +
  geom_boxplot(width = 0.3, outlier.shape = NA) +   # boxplot
  geom_half_violin(side = "l", fill = "lightgreen", alpha = 0.6, scale = "count") +  # half violin on left
  labs(
    x = "Year of Event",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ TRIM Event by Year",
    caption = "Representation by COUNT, (1st cases)"
  ) +
    scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### LGRP: What is the distribution of FIRST TRIM cases?

```{r}
#| label: Distribution of FIRST TRIM case counts by LGRP
#| 

# ==============================================================================
# Coplot of half violin and boxplot for 1st TRIM cases, 2024 + 2025, by LGRP - scale = count
# ==============================================================================

my_fills <- c(
  "LACT 1" = "lightblue",
  "LACT 2" = "lightgreen",
  "LACT 3+" = "tomato"
)

lame_trim %>%
  filter(event == "TRIM",
         lact_group != "Heifer",
         SEQ == 1,
         year_event %in% c(2024, 2025)) %>% 
  ggplot(aes(x = lact_group, y = dim_event, fill = lact_group)) +
  geom_boxplot(width = 0.3, outlier.shape = NA, alpha = 0.6) +   # boxplot parameters
  geom_half_violin(side = "l", scale = "count") +  # half violin on left
  labs(
    x = "1st TRIM, LGRP demographics (2024-2025)",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ TRIM Event by Lactation Group",
    caption = "Representation by LGRP, 1st cases & COUNT"
  ) +
  scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  scale_fill_manual(values = my_fills) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### LGRP: What is the distribution of ALL TRIM cases?

```{r}
#| label: Distribution of ALL TRIM case counts by LGRP
#| 

# ==============================================================================
# Coplot of half violin and boxplot for ALL TRIM cases, 2024 + 2025, by LGRP - scale = count
# ==============================================================================

my_fills <- c(
  "LACT 1" = "lightblue",
  "LACT 2" = "lightgreen",
  "LACT 3+" = "tomato"
)

lame_trim %>%
  filter(event == "TRIM",
         lact_group != "Heifer",
         year_event %in% c(2024, 2025)) %>% 
  ggplot(aes(x = lact_group, y = dim_event, fill = lact_group)) +
  geom_boxplot(width = 0.3, outlier.shape = NA, alpha = 0.6) +   # boxplot parameters
  geom_half_violin(side = "l", scale = "count") +  # half violin on left
  labs(
    x = "ALL TRIM, LGRP demographics (2024-2025)",
    y = "DIM @ Event Distribution",
    title = "Distribution of DIM @ TRIM Event by Lactation Group",
    caption = "Representation by LGRP, ALL cases & COUNT"
  ) +
  scale_y_continuous(
    limits = c(0, 420), 
    breaks = seq(0, 420, by = 30),
    labels = paste0(seq(0, 420, by = 30), "")
  ) +
  scale_fill_manual(values = my_fills) +
  theme(
    plot.title = element_text(hjust = 0.5)  # centers the title
  )
```

### LGRP: What is the average number of trim cases / treated cow?

```{r}
#| label: Average number of TRIMs by LGRP
#| 

# ==============================================================================
# Plot of average number of treatments by LGRP(3+) and year
# ==============================================================================


# Define custom fills
my_fills <- c(
  "LACT 1" = "lightblue",
  "LACT 2" = "lightgreen",
  "LACT 3+" = "tomato"
)

# Prepare the summarized data
lame_summary <- lame_trim %>%
  filter(event == "TRIM",
         year_event %in% c(2023, 2024, 2025)) %>%
  group_by(year_event, lact_group) %>%
  # Summarize the SEQ column for TRIM cases
  summarise(
    mean_SEQ = mean(SEQ, na.rm = TRUE),
    sd_SEQ   = sd(SEQ, na.rm = TRUE),
    n        = n(),
    .groups  = "drop"
  ) %>%
  # Determine an 80% confidence interval
  mutate(
    se = sd_SEQ / sqrt(n),
    # 80% confidence interval uses z ≈ 1.28
    ci = 1.28 * se
  )

# Plot with black borders and mean labels
ggplot(lame_summary, aes(x = factor(year_event),
                         y = mean_SEQ,
                         fill = lact_group)) +
  geom_col(position = position_dodge(width = 0.9),
           colour = "black") +
  geom_errorbar(aes(ymin = mean_SEQ - ci,
                    ymax = mean_SEQ + ci),
                width = 0.2,
                position = position_dodge(width = 0.9)) +
  geom_text(aes(label = round(mean_SEQ, 2)),   # display mean values
            position = position_dodge(width = 0.9),
            vjust = -1.2, size = 3.5) +        # adjust vertical placement
  scale_fill_manual(values = my_fills) +
  labs(
    x = "Year",
    y = "Average number of TRIM cases (SEQ)",
    fill = "Lactation Group",
    title = "Average TRIM Cases by Year and Lactation Group (2023–2025)",
    caption = "Average cases per treated cow"
  ) +
  theme_minimal()


```

```

